%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage{lato}
% \usepackage{montserrat}
% \usepackage{opensans}
% \usepackage{ebgaramond}
% \usepackage{libertine}
% \usepackage{palatino}
% \usepackage{mathpazo}
\usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.1in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% Make sure to enter your actual profile URLs
\begin{center}
    \textbf{\Huge \scshape Vishwa Govula} \\ \vspace{1pt}
    \small +91 9959888391 $|$ \href{mailto:vishwagovula07@gmail.com}{\underline{vishwagovula07@gmail.com}} $|$
    \href{https://www.linkedin.com/in/vishwa-govula-1b482a347/}{\underline{LinkedIn}} $|$
    \href{https://github.com/Wreck7}{\underline{GitHub}} $|$
    \href{https://x.com/F1Vishwa}{\underline{Twitter (X)}}
     $|$
    \href{https://vishwa7.netlify.app/}{\underline{Portfolio}}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
 \resumeSubHeadingListStart
    \resumeItem{A passionate and motivated Computer Science student specializing in full-stack web development. Possesses a strong foundation in both front-end and back-end technologies, with hands-on experience building applications from concept to deployment. Eager to apply problem-solving skills and collaborate in a dynamic team to contribute to impactful, real-world projects.}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University College of Science, Osmania University}{Hyderabad, Telangana}
      {Bachelor of Science in Computer Science (Honors)}{2023 -- 2027 (Pursuing)}
  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, TypeScript, HTML, CSS, SQL} \\
     \textbf{Frameworks \& Libraries}{: ReactJS, NodeJS, ExpressJS, FastAPI, Streamlit, Jinja2, Tailwind CSS, BootStrap, Framer Motion, WebSockets} \\
     \textbf{Databases}{: MongoDB, Mongoose(ODM), PostgreSQL, Supabase, Firebase} \\
     \textbf{Developer Tools}{: Git, GitHub, Postman}
    }}
 \end{itemize}
 

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{CryptoSim - Crypto Simulator Webapp} $|$ \emph{FastAPI, Streamlit, Supabase, PostgreSQL}}{}
          \resumeItemListStart
            \resumeItem{Developed a full-stack crypto trading simulator to provide users with a risk-free platform for practicing trading strategies.}
            \resumeItem{Engineered a back-end with FastAPI to handle user authentication, real-time coin data, and transaction logic.}
            \resumeItem{Designed a reactive front-end using Streamlit for intuitive data visualization, portfolio tracking, and trade execution.}
            \resumeItem{Utilized Supabase with PostgreSQL for robust database management, ensuring persistent user data and portfolio states.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{FolioBuilder – Portfolio Builder} $|$ \emph{React, TypeScript, TailwindCSS, Supabase
}}{}
          \resumeItemListStart
            \resumeItem{Built a no-code platform for creating and publishing responsive portfolio websites.}
            \resumeItem{Implemented dynamic UI components and animations for visually engaging, modern portfolio templates.}
            \resumeItem{Designed a scalable system architecture for seamless customization, real-time preview, and deployment.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------STRENGTHS-----------
\section{Strengths}
    \resumeSubHeadingListStart
        \resumeItem{\textbf{Collaboration:} Team player with excellent communication skills and a strong belief in collective success.}
        \resumeItem{\textbf{Adaptability:} Quick learner with the ability to rapidly master new technologies and adapt to changing project requirements.}
        \resumeItem{\textbf{Work Ethic:} Responsible, goal-oriented, and energetic with strong multi-tasking and observational skills.}
    \resumeSubHeadingListEnd

%-----------HOBBIES & INTERESTS-----------
\section{Hobbies \& Interests}
    \resumeSubHeadingListStart
        \resumeItem{Exploring AI-enhanced coding techniques with tools like GitHub Copilot.}
        \resumeItem{Sharing technical knowledge and solutions through blogging on Twitter.}
        \resumeItem{Playing Cricket, fostering teamwork and strategic thinking.}
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}